Beating Simple Backtracking Search in Subgraph Algorithms\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/026842/1 and EP/M508056/1].}

### 2018-11-26 paper/paper.tex
Dupe

The subgraph isomorphism problem is to decide whether a copy of a small ``pattern'' graph occurs
inside a larger ``target'' graph. The problem is broadly applicable, with applications in areas
including in bioinformatics \cite{o:BonniciGPSF13}, chemistry \cite{o:Regin95}, computer vision
\cite{DBLP:journals/cviu/DamiandSHJS11,DBLP:journals/pr/SolnonDHJ15}, law enforcement
\cite{DBLP:journals/cacm/CoffmanGM04}, model checking \cite{DBLP:journals/tcs/SevegnaniC15},
malware detection \cite{DBLP:conf/dimva/BruschiMM06}, compilers
\cite{DBLP:conf/cgo/MurrayF12,DBLP:conf/cp/BlindellLCS15}, pattern recognition
\cite{DBLP:journals/ijprai/FoggiaPV14}, program similarity
comparison \cite{o:DallaPredaV17}, the design of mechanical locks
\cite{DBLP:journals/siamrev/VomelLBF17}, and graph databases
\cite{DBLP:journals/jair/McCreeshPST18}.

>>>>

The subgraph isomorphism problem is to decide whether a copy of a small ``pattern'' graph occurs
inside a larger ``target'' graph. The problem is broadly applicable, with applications in areas
including in bioinformatics \cite{DBLP:journals/bmcbi/BonniciGPSF13}, chemistry \cite{o:Regin95}, computer vision
\cite{DBLP:journals/cviu/DamiandSHJS11,DBLP:journals/pr/SolnonDHJ15}, law enforcement
\cite{DBLP:journals/cacm/CoffmanGM04}, model checking \cite{DBLP:journals/tcs/SevegnaniC15},
malware detection \cite{DBLP:conf/dimva/BruschiMM06}, compilers
\cite{DBLP:conf/cgo/MurrayF12,DBLP:conf/cp/BlindellLCS15}, pattern recognition
\cite{DBLP:journals/ijprai/FoggiaPV14}, program similarity
comparison \cite{o:DallaPredaV17}, the design of mechanical locks
\cite{DBLP:journals/siamrev/VomelLBF17}, and graph databases
\cite{DBLP:journals/jair/McCreeshPST18}.
